%\input{../Informe/Header.tex}

%\begin{document}

\begin{flushleft}
\begin{thebibliography}{9}

\bibitem{ref:PaperValeriaOjeda}
V. Ojeda, M. L. Chazarreta, C. M. Pozzi. \textit{El Carpintero Gigante: Especie Clave Del Bosque Andino Patagónico}. Difundiendo Saberes, Vol. 8, 2011.

\bibitem{ref:wpteff}
Large.stanford.edu. n.d. Wireless Power Efficiency. [online] Disponible en: \href{http://large.stanford.edu/courses/2016/ph240/surakitbovorn1/}{http://large.stanford.edu/courses/2016/ph240/surakitbovorn1/} [Accedido 26 Jun 2021].

\bibitem{ref:wirelesschargingkeyelements}
Palmberg, E., Lundmark, S., Alatalo, M., Thiringer, T. and Karlsson, R., 2012. Wireless Charging - some key elements. [online] Publications.lib.chalmers.se. Disponible en: \href{https://publications.lib.chalmers.se/records/fulltext/175567/175567.pdf}{https://publications.lib.chalmers.se/records/fulltext/175567/175567.pdf} [Accedido 26 Jun 2021].

\bibitem{ref:couplingfactor_1}
Abatti, P., Pichorim, S. and de Miranda, C., 2015. Maximum Power Transfer versus Efficiency in Mid-Range Wireless Power Transfer Systems. Journal of Microwaves, Optoelectronics and Electromagnetic Applications, 14(1), pp.97-109.

\bibitem{ref:NearFieldVsFarField}
Occupational Safety and Health Administration, Cincinnati Technical Center (May 20, 1990). "Electromagnetic Radiation and How It Affects Your Instruments. Near field vs. Far field" Disponible en: \href{https://www.osha.gov/radiofrequency-and-microwave-radiation/electromagnetic-field-memo}{https://www.osha.gov/radiofrequency-and-microwave-radiation/electromagnetic-field-memo} [Accedido 25 Jun 2021].

\bibitem{ref:NearFieldUHFRFID}
V. Nikitin, P., Rao, K. and Lazar, S., n.d. An Overview of Near Field UHF RFID.

\bibitem{ref:PhysicsOscillations}
Vistnes, A., 2018. Physics of Oscillations and Waves. Oslo, Norway: Springer, Chapter 9.

\bibitem{ref:Humavox}
Humavox. n.d. Our Technology – Humavox. [online] Available at: \href{http://www.humavox.com/our-technology/}{http://www.humavox.com/our-technology/} [Accedido 27 June 2021].

\bibitem{ref:ITUISM}
Life.itu.int. n.d. Terms and definitions. [online] Disponible en: \href{https://life.itu.int/radioclub/rr/art1.pdf}{https://life.itu.int/radioclub/rr/art1.pdf} [Accedido 26 Jun 2021].

\bibitem{ref:ITUREGION}
Sma.gov.jm. n.d. ITU Radio Regulations, CHAPTER II – Frequencies, ARTICLE 5 Frequency allocations, Section IV – Table of Frequency Allocations. [online] Disponible en: \href{https://www.sma.gov.jm/sites/default/files/publication_files/ITU-R_Radio_Regulations_2012_\%202015_\%20Article_5_Table\%20of\%20Frequencies.pdf}{https://www.sma.gov.jm/sites/default/files/publication\_files/ITU-R\_Radio\_Regulations\_2012\_\%202015\_\%20Article\_5\_Table\%20of\%20Frequencies.pdf} [Accedido 26 Jun 2021].

\bibitem{ref:Penguin}
L. Upton, 2014. Penguin Lifelines. [Blog] Raspberry Pi Blog, Disponible en: \href{https://www.raspberrypi.org/blog/penguin-lifelines/}{https://www.raspberrypi.org/blog/penguin-lifelines/} [Accedido 24 May 2021].


\bibitem{ref:rpicam}
``Raspberry Pi Documentation - Camera'', Raspberrypi.org, 2021. [Online]. Disponible en: \href{https://www.raspberrypi.org/documentation/accessories/camera.html}{https://www.raspberrypi.org/documentation/accessories/camera.html}. [Accedido 05  Oct 2021].

\bibitem{ref:weather_bariloche}
``El tiempo en San Carlos de Bariloche en la primavera, temperatura promedio (Argentina) - Weather Spark'', Es.weatherspark.com, 2021. [Online]. Disponible en: \href{https://es.weatherspark.com/s/25786/0/Tiempo-promedio-en-la-primavera-en-San-Carlos-de-Bariloche-Argentina}{https://es.weatherspark.com/s/25786/0/Tiempo-promedio-en-la-primavera-en-San-Carlos-de-Bariloche-Argentina}. [Accedido 05 Oct 2021].
\end{thebibliography}
\end{flushleft}

%\end{document}
